GMSE: a general tool for management strategy evaluation

### 2017-09-14 notebook/presentation/GMSE_presentation.Rmd
New structures and before-after image

@@

@@

- How to solve conflict
- What leads to conflict
- Impact on sustainability

@@

## Point about conflict and games being complex

Nils points out that typical game theory assumes that

@@

- Objective of GMSE 1
- Objective of GMSE 2
- Objective of GMSE 3

@@

- Technical detail of GMSE 1
- Technical detail of GMSE 2
- Technical detail of GMSE 3

>>>>

![](mannahatta_before.jpg)

@@

**Conservation conflicts are complex, and characterised by incomplete information that is rapidly changing.**

@@

- What leads to conflict
- How to solve conflict
- Impact on sustainability

@@

## Simple game-theoretic models insufficient

@@

- Integrates game theory and ecological theory to construct social-ecological models for adaptive management
- Simulates all aspects of management: population dynamics, manager observation of populations, manager decision making, and stakeholder responses to management decisions
- Mimic the decision-making process of managers and stakeholders under conditions of change, uncertainty, and conflict
- Provide a flexible modelling framework for future development of complex adaptive management models to be applied to conservation theory and specific case studies

@@

- Written in R and C
- Requires R (>= 3.3.3)
- License GPL (>=2)
